### 2020-03-29 document/manuscript-out.tex
Travis build: 130

>>>>

\subsubsection{Draft text for the
section}\label{draft-text-for-the-section}

Access to literature is of paramount importance in the process of
scientific inquiry. The free flow of ideas and information are crucial
to addressing economic, environmental and social issues facing
developing countries especially in Africa. However, contrary to
concerted research efforts to foster development, an assessment of
Africa's research output between 1999 - 2008 indicated that Africa
lagged behind in it's research output when compared to the rest of the
world \cite{adams2010;raju2012}. Poor accessibility of scientific
publications has been suggested as one of the reasons for the low
research output from Africa \cite{tise2011;raju2012}.
